---
title: "CVAX RNASeq Analysis - Model"
author: "E. Kelley"
date: "5/5/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE, echo = TRUE)
library(tidyverse)
library(DESeq2)
```

Using LRT for time series data with subject_id in the reduced model.
```{r apply LRT for time series analysis}
# cvax_de_data <- DESeq(cvax_de_data, test="LRT", reduced=~subject_id)

# saveRDS(cvax_de_data, "CVAX_RNASeq_run001/cvax_de_data_all_subjects.rds")

cvax_de_data <- readRDS("CVAX_RNASeq_run001/cvax_de_data_all_subjects.rds")
```


In general, the results for a comparison of any two levels of a variable can be extracted using the contrast argument to results. The user should specify three values: the name of the variable, the name of the level in the numerator, and the name of the level in the denominator. Here we extract results for the log2 of the fold change of DPN / Control.
```res <- results( dds, contrast = c("treatment", "DPN", "Control") )```

```{r}
cvax_results_8v0 <- results(cvax_de_data, contrast = c("days_from_first_dose", "8", "0"))

cvax_results_8v0_ordered <- cvax_results_8v0[order(cvax_results_8v0$padj), ]

# added the hgnc_symbol column to results df
res_df <- bind_cols(as.data.frame(cvax_results_8v0), cvax_results_8v0$hgnc_symbol)

# write.csv(as.data.frame(cvax_results_8v0_ordered),"CVAX_RNASeq_run001/CVAX_results_8v0_ordered.csv", row.names = T)
```



```{r add hgnc symbol to cvax 8v0 results}
# From the DESeq2 beginners guide
cvax_results_8v0$ensembl <- rownames(cvax_results_8v0)

ensembl=useMart("ensembl", dataset = "hsapiens_gene_ensembl")

genemap <- getBM( attributes = c("ensembl_gene_id", "hgnc_symbol"),
filters = "ensembl_gene_id", 
values = rownames(cvax_results_8v0),
mart = ensembl )
no_hgnc <- genemap$hgnc[genemap$hgnc_symbol == ""] # 7025 ENSG w/ missing hgnc_symbol, leaving 22611 ENSG w/ hgnc symbol

idx <- match(rownames(cvax_results_8v0), genemap$ensembl_gene_id) 

cvax_results_8v0$hgnc_symbol <- genemap$hgnc_symbol[ idx ]

```


```{r}
# add entrez id's to the data

# From the DESeq2 beginners guide

ensembl=useMart("ensembl", dataset = "hsapiens_gene_ensembl")

genemap2 <- getBM(attributes = c("ensembl_gene_id", "entrezgene_id"),
filters = "ensembl_gene_id", 
values = rownames(cvax_results_8v0),
mart = ensembl)

# no_hgnc <- genemap$hgnc[genemap$hgnc_symbol == ""] # 7353 ENSG w/ missing hgnc_symbol, leaving 22611 ENSG w/ hgnc symbol

idx2 <- match(rownames(cvax_results_8v0), genemap$ensembl_gene_id) 

cvax_results_8v0$entrezid <- genemap2$entrezgene_id[ idx2 ]
```




```{r day 8 contrasts}
cvax_results_8v0_ordered <- cvax_results_8v0[order(cvax_results_8v0$padj), ]
res_8v0_df <- as.data.frame(cvax_results_8v0_ordered)

# write.csv(as.data.frame(cvax_results_8v0_ordered),"CVAX_RNASeq_run001/CVAX_results_8v0.csv", row.names = T)
```


```{r extract day 28 contrasts}
cvax_results_28v0 <- results(cvax_de_data, contrast = c("days_from_first_dose", "28", "0"))
```

```{r add hgnc symbol to cvax 28v0 results}
# From the DESeq2 beginners guide
cvax_results_28v0$ensembl <- rownames(cvax_results_28v0)

ensembl=useMart("ensembl", dataset = "hsapiens_gene_ensembl")

genemap <- getBM( attributes = c("ensembl_gene_id", "hgnc_symbol"),
filters = "ensembl_gene_id", 
values = rownames(cvax_results_28v0),
mart = ensembl )
no_hgnc <- genemap$hgnc[genemap$hgnc_symbol == ""] # 7353 ENSG w/ missing hgnc_symbol, leaving 22611 ENSG w/ hgnc symbol

idx <- match(rownames(cvax_results_28v0), genemap$ensembl_gene_id) 

cvax_results_28v0$hgnc_symbol <- genemap$hgnc_symbol[ idx ]

```



```{r day 28 contrasts}
cvax_results_28v0_ordered <- cvax_results_28v0[order(cvax_results_28v0$padj), ]
res_28v0_df <- as.data.frame(cvax_results_28v0_ordered)

# write.csv(as.data.frame(cvax_results_28v0_ordered),"CVAX_RNASeq_run001/CVAX_results_28v0.csv", row.names = T)

# write.csv(res_8v0_df, "CVAX_RNASeq_run001/CVAX_results_all_subjects_8v0.csv", row.names = T)
# write.csv(res_28v0_df, "CVAX_RNASeq_run001/CVAX_results_all_subjects_28v0.csv", row.names = T)
```



